\Large Feature and order manipulations in a free recall task affect memory for current and future lists

### 2023-01-24 paper/main.tex
added darya as a co-author, removed kirsten as a co-author (by her request, per email on 1/23/23)

\author{Jeremy R. Manning\textsuperscript{1, *}, Kirsten
Ziman\textsuperscript{1, 2}, Emily Whitaker\textsuperscript{1},\\Paxton C.
Fitzpatrick\textsuperscript{1}, Madeline R. Lee\textsuperscript{1}, Allison M
Frantz\textsuperscript{1},\\Bryan J. Bollinger\textsuperscript{1}, Campbell E.
Field\textsuperscript{1}, and Andrew C. Heusser\textsuperscript{1,
3}\\\textsuperscript{1}Dartmouth College\\\textsuperscript{2}Princeton
University\\\textsuperscript{3}Akili
Interactive\\\textsuperscript{*}Corresponding author:
jeremy.r.manning@dartmouth.edu}

@@

Conceptualization: JRM and ACH. Methodology: JRM and ACH. Software: JRM, KZ,
PCF, CEF, and ACH. Analysis: JRM, PCF, and ACH. Data collection: KZ, EW, PCF,
MRL, AMF, BJB, and CEF. Data curation and management: KZ, EW, PCF, MRL, ACH.
Writing (original draft): JRM. Writing (review and editing): KZ, EW, PCF, MRL,
AMF, BJB, CEF, and ACH. Supervision: JRM and ACH. Project administration: KZ,
EW, and PCF. Funding acquisition: JRM.

@@

We acknowledge useful discussions, assistance in setting up an earlier
(unpublished) version of this study, and assistance with some of the data
collection efforts from Rachel Chacko, Joseph Finkelstein, Sheherzad Mohydin,
Lucy Owen, Gal Perlman, Darya Romanova, Jake Rost, Jessica Tin, Marisol Tracy,
and Peter Tran. Our work was supported in part by NSF CAREER Award Number
2145172 to JRM. The content is solely the responsibility of the authors and
does not necessarily represent the official views of our supporting
organizations. The funders had no role in study design, data collection and
analysis, decision to publish, or preparation of the manuscript.

>>>>

\author{Jeremy R. Manning\textsuperscript{1, *}, Emily
Whitaker\textsuperscript{1}, Paxton C. Fitzpatrick\textsuperscript{1},
\\Madeline R. Lee\textsuperscript{1}, Allison M. Frantz\textsuperscript{1},
Bryan J. Bollinger\textsuperscript{1},\\Darya Romanova\textsuperscript{1},
Campbell E. Field\textsuperscript{1}, and Andrew C. Heusser\textsuperscript{1,
2}\\\textsuperscript{1}Dartmouth College\\\textsuperscript{2}Akili
Interactive\\\textsuperscript{*}Corresponding author:
jeremy.r.manning@dartmouth.edu}

@@

Conceptualization: JRM and ACH. Methodology: JRM and ACH. Software: JRM, PCF,
CEF, and ACH. Analysis: JRM, PCF, and ACH. Data collection: EW, PCF, MRL, AMF,
BJB, DR, and CEF. Data curation and management: EW, PCF, MRL, ACH. Writing
(original draft): JRM. Writing (review and editing): EW, PCF, MRL, AMF, BJB,
DR, CEF, and ACH. Supervision: JRM and ACH. Project administration: EW, and
PCF. Funding acquisition: JRM.

@@

We acknowledge useful discussions, assistance in setting up an earlier
(unpublished) version of this study, and assistance with some of the data
collection efforts from Rachel Chacko, Joseph Finkelstein, Sheherzad Mohydin,
Lucy Owen, Gal Perlman, Jake Rost, Jessica Tin, Marisol Tracy,
Peter Tran, and Kirsten Ziman. Our work was supported in part by NSF CAREER Award Number
2145172 to JRM. The content is solely the responsibility of the authors and
does not necessarily represent the official views of our supporting
organizations. The funders had no role in study design, data collection and
analysis, decision to publish, or preparation of the manuscript.
